---
title       : Developing Data Products Project Slidify Presentation
subtitle    : New York Air Quality Variables
author      : TheaBao
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Description

The Dataset used in this project contains daily air quality measurements in New York, May to September 1973.
```{r, echo=TRUE}
library(datasets)
head(airquality)
```
The datatable shows 154 observations on 6 variables.

--- .class #id 

## Variables

*Variables tracked in the data table are explained below:*

-**Ozone**: Mean ozone in parts per billion from 1300 to 1500 hours at Roosevelt Island

-**Solar.R**: Solar radiation in Langleys in the frequency band 4000 to 7700 Angstroms from 0800 to 1200 hours at Central Park

-**Wind**: Average wind speed in miles per hour at 0700 and 1000 hours at LaGuardia Airport

-**Temp**: Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.

-Also **Month** and **Day**.

*I will examine the relationship between each variable with the temperature of the day, using the shiny model: https://theabao.shinyapps.io/Shiny*

--- .class #id 

## Regression Model Plots
```{r,fig.height=4,fig.width=14}
data<-airquality
par(mfrow=c(1,5))
plot(Ozone, Temp, main="Temp ~ Ozone", )
plot(Solar.R, Temp, main="Temp ~ Solar.R")
plot(Wind, Temp, main="Temp ~ Wind")
plot(Month, Temp, main="Temp ~ Month")
plot(Day, Temp, main="Temp ~ Day")
```

--- .class #id 

## Results
```{r,echo=FALSE,fig.height=4,fig.width=14}
data<-airquality
par(mfrow=c(1,5))
plot(Ozone, Temp, main="Temp ~ Ozone", abline(lm(Temp~Ozone), col=2))
plot(Solar.R, Temp, main="Temp ~ Solar.R", abline(lm(Temp~Solar.R), col=2))
plot(Wind, Temp, main="Temp ~ Wind", abline(lm(Temp~Wind), col=2))
plot(Month, Temp, main="Temp ~ Month", abline(lm(Temp~Month), col=2))
plot(Day, Temp, main="Temp ~ Day", abline(lm(Temp~Day), col=2))
```

Positively related variables with temperature: Ozone, Solar.R and Month;
negatively related variables with temperature: Wind and Day

The end.
--- .class #id 
